\documentclass{article}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{etoolbox}
\usepackage[normalem]{ulem}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{url}
%% \usepackage{enumerate}
\input{../macros.sty}
\author{Brandon A. Mayer}
\title{\sciwms{} CI-2014 Book Chapter Outline}
\date{}

\newbool{commentson}
\booltrue{commentson}
\ifbool{commentson}
{
  \long\def\commentbam#1{{\color{red}\bf **Brandon: #1**}}
  %%Just in case Brian is compelled to comment.
  \long\def\commentbm#1{{\color{green}\bf **Brian: #1**}}
}
{
  \long\def\commentb#1{{}}
  \long\def\commentm#1{{}}
}

\begin{document}
\maketitle

\section{Motivation}
\begin{enumerate}
  \item What is the problem?
  \item Why is the problem important?
  \item How does \sciwms{} solve the problem?
  \item State Novelties and Contributions
    \begin{enumerate}[label*=\arabic*.]
      \item Support for arbitrary projections specified by client through EPS string.
      \item \sciwms{} is the first WMS to support unstructured CF-Compliant data.
    \end{enumerate}
\end{enumerate}

\section{\sciwms{}}
\begin{enumerate}
  \item Overview of OpenGIS WMS specification
    \begin{enumerate}[label*=\arabic*.]
      \item What is a WMS specification?
      \item getCapabilities, getFeatureInfo, and getMap
      \item Standard Http Interface
      \item REST-like API for client-server seperation
    \end{enumerate}
  \item Overview of CF-Standard
    \begin{enumerate}[label*=\arabic*.]
      \item Standard names for Atmospheric, Climate, Weather and Forcasting data
    \end{enumerate}

  \item Overview of Grid Types and Models
    \begin{enumerate}[label*=\arabic*.]
      \item ADCIRC      
      \item SELFE
      \item FVCOM
      \item SLOSH
      \item ROMS
    \end{enumerate}

  \item Overview of R-Tree Database
    \begin{enumerate}
      \item WMS getMap requests are orthogonal range queries, ideally suited for Rtree datastructures
      \item Rtree figure?
      \item Create local cache of unstructured grid points using Rtree database
      \item Run time of creation
      \item Run time analysis of query
      \item Each getMap request finds the indices of the appropriate data in optimal time
        via queries to the Rtree database.
    \end{enumerate}
\end{enumerate}

\section{COMT-IOOS Deployment}
\begin{enumerate}
  \item Mission of COMT-IOOS
  \item Use case of federated dataset hosted at multiple organizations unified by a CSW catalogue.
  \item \sciwms{} deployed for qualitative parameter selection, skill assessment and model comparison.
\end{enumerate}
\end{document}
